Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-18 mr-review.Rmd
word fix

Complex trait genetics studies in humans have yielded thousands of new associations for  
diverse traits. The next step in understanding biology of health and disease is to
identify causal relationships among complex traits. Two-sample Mendelian randomization studies 
in genome-wide association studies can uncover causal relationships 
between complex traits. By leveraging shared SNP genotypes as instrumental variables, or proxies, for 
the exposure complex trait, investigators can tease out causal effects from observational data, provided
that three assumptions are satisfied. We discuss below the growth of genome-wide association studies 
in parallel with development of Mendelian randomization methods. We argue that the recent availability of GWAS summary statistics for diverse complex traits has led to new Mendelian randomization methods and that this area continues to offer opportunities for additional methods developments.

>>>>

Complex trait genetics studies in humans have yielded thousands of new associations for  
diverse traits. The next step in understanding biology of health and disease is to
identify causal relationships among complex traits. Two-sample Mendelian randomization studies 
in genome-wide association studies can uncover causal relationships 
between complex traits. By leveraging shared SNP genotypes as instrumental variables, or proxies, for 
the exposure complex trait, investigators can tease out causal effects from observational data, provided
that three assumptions are satisfied. We discuss below the growth of genome-wide association studies 
in parallel with development of Mendelian randomization methods. We argue that the recent availability of GWAS summary statistics for diverse complex traits has motivated new Mendelian randomization methods and that this area continues to offer opportunities for additional methods developments.
